### 2016-03-14 paper/result_stereo.tex
Hang
results

We performed our experiments on the Book sequence from Middlebury stereo
datasets.~\cite{middlebury_stereo}. We use 7 images with the
resolution of $695\times555$ and optimize for 256 disparity labels. We
recoreded both single thread energy and system energy (minimum energy
so far from all threads) against time. Since the order of labels to be
expanded or fused will have impact on minimization, we randomly
shuffled 256 labels and provide this order to all methods.

\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_global.eps}
  \caption{The energy minimization process of difference parallel systems.}
  \label{fig:stereo_global}
\end{figure}

@@

Figure \ref{fig:stereo_global} shows the energy minimization process
against time. In this experiment, both PAE and SF-MF converge faster
than sequential method. However, since fusing solutions with multiple
labels by QPBO is slower than a single $\alpha$-expansion, PAE method
reaches convergence faster than SF-MF. Architectures with multiway
fusion, e.g. SF and SF-SS perform worse than PAE and SF-MF, because
the TRWS algorihtm used in multiway fusion is slower than multiple
$\alpha$-expansion. Finally, the line of hierarchy fusion only makes
jump when fusing on root node of the tree. This is because any fusion
step on non-root nodes only have partial label information.

@@

For a easy optimization problem as shown in this section, our full
architecture with solution sharing and multiway fusion actually makes
convergence slower by adopting sophisticated algorihtm and introducing
multi-threading overhead. However, we can easily configure the
architecture to make it better fit the problem, e.g. turn off multiway
fusion and/or solution sharing.

\hang{The end of stereo experiment......}

>>>>

We performed our experiments on the Book sequence from Middlebury
stereo datasets.~\cite{middlebury_stereo}. We use 7 images with the
resolution of $695\times555$ and optimize for 256 disparity labels. We
recoreded both single thread energy and system energy against
time. Since the order of labels to be expanded or fused will have
impact on minimization, we randomly shuffled 256 labels and provide
this order to all methods. In PAE, SF-MF, SF-SS and SF algorithms, the
proposal generator in each thread can only generate constant-label
proposals within a evenly split subset of all labels.

\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_global.png}
  \caption{The energy minimization process of difference parallel systems.}
  \label{fig:stereo_global}
\end{figure}

@@

Figure \ref{fig:stereo_global} shows the energy minimization process
against time. In this experiment, both PAE and SF-MF converge faster
than sequential method. However, since fusing solutions with multiple
labels by QPBO is slower than a single $\alpha$-expansion, PAE method
reaches convergence faster than SF-MF. Architectures with multiway
fusion, e.g. SF and SF-SS perform worse than PAE and SF-MF, because
the TRWS algorihtm used in multiway fusion is slower than multiple
$\alpha$-expansions. Finally, the line of hierarchy fusion only makes
jump when fusing on root node of the tree. This is because any fusion
step on non-root nodes only have partial label information.

@@

For an easy optimization problem as stereo with submodular energy, our
full architecture with solution sharing and multiway fusion actually
makes convergence slower due too over-sophisticated fusion algorihtm
and multi-threading overhead. However, we can easily configure the
architecture to make it better fit the problem, e.g. turn off multiway
fusion and/or solution sharing.

### 2016-03-14 paper/results.tex
Hang

\section{Experimental results}
\label{section:results}
We have implemented the algorithms with multithreading supporting from
C++ 11 and conducted the experiments on Linux PCs with Intel Core i7
4790 processor with 4 cores, enabling 8 threads with the hyper
threading technology. We have used the Graph-cuts optimization code
written by Veksler, using the libraries provided by Boykov and
Kolmogorov~\cite{middlebury_mrf,alpha_expansion,what_energy_can_be_min_by_gc, mrf_experimental}.
% [2] Fast Approximate Energy Minimization via Graph Cuts.
%         Y. Boykov, O. Veksler, and R. Zabih.
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 23, no. 11, pages 1222-1239, November 2001.  
%
%     [3] What Energy Functions can be Minimized via Graph Cuts?
%         V. Kolmogorov and R. Zabih. 
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 26, no. 2, pages 147-159, February 2004. 
%         An earlier version appeared in European Conference on Computer
%         Vision (ECCV), May 2002.
%
%     [4] An Experimental Comparison of Min-Cut/Max-Flow Algorithms for
%         Energy Minimization in Vision. 
%         Y. Boykov and Vladimir Kolmogorov.
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 26, no. 9, pages 1124-1137, September 2004. 
We have used the QPBO and TRW-S implementations by
Kolmogorov~\cite{QPBO, TRW-S_implementation}.

>>>>

\section{Experimental results}
\label{section:results}
We have implemented the algorithms with multithreading supporting from
C++ 11 and conducted the experiments on Linux PCs with Intel Core i7
4790 processor with 4 cores. We have used the Graph-cuts optimization
code written by Veksler, using the libraries provided by Boykov and
Kolmogorov~\cite{middlebury_mrf,alpha_expansion,what_energy_can_be_min_by_gc,mrf_experimental}.
% [2] Fast Approximate Energy Minimization via Graph Cuts.
%         Y. Boykov, O. Veksler, and R. Zabih.
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 23, no. 11, pages 1222-1239, November 2001.  
%
%     [3] What Energy Functions can be Minimized via Graph Cuts?
%         V. Kolmogorov and R. Zabih. 
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 26, no. 2, pages 147-159, February 2004. 
%         An earlier version appeared in European Conference on Computer
%         Vision (ECCV), May 2002.
%
%     [4] An Experimental Comparison of Min-Cut/Max-Flow Algorithms for
%         Energy Minimization in Vision. 
%         Y. Boykov and Vladimir Kolmogorov.
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 26, no. 9, pages 1124-1137, September 2004. 
We have used the QPBO and TRW-S implementations by
Kolmogorov~\cite{QPBO, TRW-S_implementation}.

To evaluate the effectness of different parallel structures, we plot
the energy minimization process against time. We define the energy of
a parallel optimization system at a certain time as the minimum energy
of all threads at that time.

### 2016-03-14 paper/stereo.tex
Hang

\section{Swarm Fusion instantiation}
We compare SF against competing approaches over three problems in
Computer Vision. SF framework has high degrees of freedom and the
challenge is to properly quantify the contributions of various
algorithmic aspects. For this purpose, we have used the three SF
architectures illustrated in Fig.~\ref{fig:model}.
%% For some problems, we have further limited the capabilities of SF
%% on purpose, to enable effective and fair comparative
%% evaluations. We now explain the details of the three problems.

\hang{Better to explain the methology we used, either here or in
  Result part. For example:}

\hang{To evaluate the effectness of different parallel structures, we
  plot the energy minimization process against time. We define the
  energy of a parallel system at a certain time as the minimum energy
  of all threads at that time.}

>>>>

\section{Swarm Fusion instantiation}
\hang{I didn't understand the organization of this section at the
  first glance. Should it be clearer if we put 'Swarm fusion
  architectures' in front of 'Competing methods' in each problem?}

We compare SF against competing approaches over three problems in
Computer Vision. SF framework has high degrees of freedom and the
challenge is to properly quantify the contributions of various
algorithmic aspects. For this purpose, we have used the three SF
architectures illustrated in Fig.~\ref{fig:model}.
%% For some problems, we have further limited the capabilities of SF
%% on purpose, to enable effective and fair comparative
%% evaluations. We now explain the details of the three problems.
